### 2023-11-02 thesis/sections/5-grounding.tex
results

        {1000} & {1000}   & {15}     & {99\%}                              & {98,5\%}                            & {0\%}                                    & {69\%}        & {89\%}          & {2\%}        & {93\%}        & {81\%}        & {4\%}        \\

@@

                 &          & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}} & \multicolumn{3}{c}{\textbf{CLEVR color}}                                                                                         \\\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}

@@

        {100}    & {10}     & {\%}                                & {\%}                                & {\%}                                     & {65\%}        & {88\%}      & {2\%}       & {92\%}        & {81\%}      & {3\%}       \\
        {100}    & {15}     & {78\%}                              & {71,99\%}                           & {11\%}                                   & {62\%}        & {86,47\%}   & {2\%}       & {92\%}        & {81\%}      & {4\%}       \\
        {100}    & {30}     & {68\%}                              & {42,79\%}                           & {4\%}                                    & {65\%}        & {87,99\%}   & {2\%}       & {92\%}        & {81\%}      & {4\%}       \\
        {500}    & {10}     & {83\%}                              & {79,95\%}                           & {6\%}                                    & {67\%}        & {88\%}      & {2\%}       & {93\%}        & {82\%}      & {4\%}       \\
        {500}    & {15}     & {83\%}                              & {79,5\%}                            & {7\%}                                    & {69\%}        & {89,5\%}    & {2\%}       & {93\%}        & {82\%}      & {3\%}       \\
        {500}    & {30}     & {84\%}                              & {83,43\%}                           & {5\%}                                    & {68\%}        & {88\%}      & {2\%}       & {93\%}        & {82\%}      & {3\%}       \\
        {1000}   & {10}     & {84\%}                              & {82,42\%}                           & {5\%}                                    & {67\%}        & {88,99\%}   & {2\%}       & {93\%}        & {82\%}      & {3\%}       \\
        {1000}   & {15}     & {85\%}                              & {82,42\%}                           & {5\%}                                    & {69\%}        & {89\%}      & {2\%}       & {93\%}        & {81\%}      & {4\%}       \\
        {1000}   & {30}     & {85\%}                              & {82,81\%}                           & {4\%}                                    & {59\%}        & {85,5\%}    & {2\%}       & {93\%}        & {81\%}      & {4\%}       \\
        {1500}   & {10}     & {84\%}                              & {81,42\%}                           & {4\%}                                    & {61\%}        & {87\%}      & {2\%}       & {92\%}        & {81\%}      & {4\%}       \\
        {1500}   & {15}     & \textbf{85\%}                       & \textbf{84,43\%}                    & \textbf{4\%}                             & {69\%}        & {89,5\%}    & {2\%}       & {93\%}        & {82\%}      & {4\%}       \\
        {1500}   & {30}     & {84\%}                              & {80,95\%}                           & {4\%}                                    & {69\%}        & {89\%}      & {2\%}       & {93\%}        & {81\%}      & {4\%}       \\
        {2000}   & {10}     & {83\%}                              & {82,89\%}                           & {4\%}                                    & {61\%}        & {87\%}      & {2\%}       & {92\%}        & {81\%}      & {4\%}       \\
        {2000}   & {15}     & {84\%}                              & {81,89\%}                           & {4\%}                                    & {69\%}        & {89,5\%}    & {2\%}       & {93\%}        & {82\%}      & {4\%}       \\
        {2000}   & {30}     & {85\%}                              & {82,95\%}                           & {4\%}                                    & {69\%}        & {89\%}      & {2\%}       & {93\%}        & {81\%}      & {4\%}       \\
        {3000}   & {10}     & {82\%}                              & {79,89\%}                           & {4\%}                                    & {61\%}        & {87\%}      & {2\%}       & {92\%}        & {81\%}      & {4\%}       \\
        {3000}   & {15}     & {85\%}                              & {81,89\%}                           & {4\%}                                    & {69\%}        & {89,5\%}    & {2\%}       & {93\%}        & {82\%}      & {4\%}       \\
        {3000}   & {30}     & {83\%}                              & {80,89\%}                           & {3\%}                                    & {69\%}        & {89\%}      & {2\%}       & {93\%}        & {81\%}      & {4\%}       \\

@@

>>>>

        {1000} & {1000}   & {15}     & {99\%}                              & {98,5\%}                            & {0\%}                                    & {68\%}        & {89\%}          & {2\%}        & {93\%}        & {81\%}        & {4\%}        \\

@@

                 &          & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}} & \multicolumn{3}{c}{\textbf{CLEVR color}}                                                                                         \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}

@@

        {100}    & {10}     & {81\%}                              & {75,95\%}                           & {9\%}                                    & {21\%}        & {57\%}      & {23\%}      & {16\%}        & {37\%}      & {31\%}      \\
        {100}    & {15}     & {78\%}                              & {71,99\%}                           & {11\%}                                   & {17\%}        & {52,98\%}   & {25\%}      & {26\%}        & {43,49\%}   & {30\%}      \\
        {100}    & {30}     & {83\%}                              & {78,99\%}                           & {7\%}                                    & {19\%}        & {54,46\%}   & {24\%}      & {29\%}        & {45,49\%}   & {26\%}      \\
        {500}    & {10}     & {83\%}                              & {79,95\%}                           & {6\%}                                    & {27\%}        & {61,98\%}   & {16\%}      & {17\%}        & {38,49\%}   & {32\%}      \\
        {500}    & {15}     & {83\%}                              & {79,5\%}                            & {7\%}                                    & {28\%}        & {63,5\%}    & {16\%}      & {21\%}        & {40\%}      & {31\%}      \\
        {500}    & {30}     & {84\%}                              & {83,43\%}                           & {5\%}                                    & {30\%}        & {63,98\%}   & {17\%}      & {21\%}        & {40\%}      & {31\%}      \\
        {1000}   & {10}     & {84\%}                              & {82,42\%}                           & {5\%}                                    & {31\%}        & {65,5\%}    & {13\%}      & {12\%}        & {32,12\%}   & {34\%}      \\
        {1000}   & {15}     & {85\%}                              & {82,42\%}                           & {5\%}                                    & {31\%}        & {64,5\%}    & {16\%}      & {16\%}        & {37\%}      & {32\%}      \\
        {1000}   & {30}     & {85\%}                              & {82,81\%}                           & {4\%}                                    & {31\%}        & {63,98\%}   & {17\%}      & {13\%}        & {36\%}      & {34\%}      \\
        {1500}   & {10}     & {84\%}                              & {81,42\%}                           & {4\%}                                    & {33\%}        & {67,47\%}   & {14\%}      & {12\%}        & {33,43\%}   & {34\%}      \\
        {1500}   & {15}     & {85\%}                              & {84,43\%}                           & {4\%}                                    & {35\%}        & {68,99\%}   & {12\%}      & {17\%}        & {38,49\%}   & {31\%}      \\
        {1500}   & {30}     & {84\%}                              & {80,95\%}                           & {4\%}                                    & {36\%}        & {68,99\%}   & {15\%}      & {14\%}        & {36,97\%}   & {33\%}      \\
        {2000}   & {10}     & {83\%}                              & {82,89\%}                           & {4\%}                                    & {36\%}        & {69\%}      & {13\%}      & {13\%}        & {36\%}      & {34\%}      \\
        {2000}   & {15}     & {84\%}                              & {81,89\%}                           & {4\%}                                    & {34\%}        & {67\%}      & {14\%}      & {14\%}        & {33,31\%}   & {33\%}      \\
        {2000}   & {30}     & {85\%}                              & {82,95\%}                           & {4\%}                                    & {32\%}        & {65,5\%}    & {16\%}      & {18\%}        & {39\%}      & {32\%}      \\
        {3000}   & {10}     & {82\%}                              & {79,89\%}                           & {4\%}                                    & {34\%}        & {68\%}      & {12\%}      & {12\%}        & {32,31\%}   & {34\%}      \\
        {3000}   & {15}     & {85\%}                              & {81,89\%}                           & {4\%}                                    & {32\%}        & {65,5\%}    & {15\%}      & {13\%}        & {32,73\%}   & {35\%}      \\
        {3000}   & {30}     & {83\%}                              & {80,89\%}                           & {3\%}                                    & {30\%}        & {63,5\%}    & {16\%}      & {12\%}        & {32,73\%}   & {34\%}      \\

@@

    \caption{Overall accuracies (Acc.), F1-Score (F1) and non-target accuracies (NT) of the masked caption generator: $LSTM_o$ are different LSTM output sizes and $LSTM_e$ are different embedding sizes for the tokens in the LSTM.}
